---
title: "Quarto Example"
author: "Ramin Rzayev"
date: "15/04/2024"
output:
  quarto::quarto_html: default
  quarto::quarto_pdf: default
  quarto::quarto_word: default
---
install.packages("quarto")
library (quarto)
# Quarto Example

This is an example of a Quarto document showcasing its features.

## Introduction

Quarto is a modern document format that allows you to seamlessly integrate code, text, and visualizations.

### R Code Chunk

```{r}
# Generate some random data
set.seed(123)
x <- rnorm(280)

# Summary statistics
summary(x)
```



### Inline Code

You can also include inline code, like this: `r mean(x)`.


### Equations

Quarto supports LaTeX-style equations:

The formula for the area of a circle is $A = \pi r^2$.

## Data Visualization

### Plotting with R

```{r}
# Load the iris dataset
data(iris)

# Scatter plot of iris dataset
plot(iris$Sepal.Length, iris$Sepal.Width, 
     main = "Sepal Length vs. Sepal Width",
     xlab = "Sepal Length", ylab = "Sepal Width", 
     col = iris$Species)
legend("topright", legend = levels(iris$Species), col = 1:3, pch = 1)
```


### Tables

You can also create tables in Quarto:


```{r}
# Create a sample data frame
df <- data.frame(
  Name = c("Mike", "Asif", "Santiago"),
  Age = c(45, 22, 25),
  Country = c("USA", "Azerbaijan", "Spain")
)

# Display the data frame
knitr::kable(df, caption = "Sample Data")

```






